A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-05-11 tex/body.tex
commented out remark for now
reintroduced para in modified form

\ourparagraph{Phase 2: Applying Acyclicity and Uniqueness \beforefig(\figurename~\ref{fig:ab-rules}).}
%For presentation of the rules in this phase, we rely on a representation of terms in the $\mu$-notation.
%The premises of the rules that make up the second phase refer to
We describe the rules in this phase in terms of a mapping $\Val$
that associates with each equivalence class a $\mu$-term as its representative.
\rem{Not explicitly constructed, add here?}

@@

By Theorems~\ref{thm:t},~\ref{thm:rs}, and~\ref{thm:ss}, the
calculus is sound and complete for the universal theory of (co)datatypes. We can
rightly call it a decision procedure for that theory.
We remark that the proof of solution soundness is constructive,
meaning that it provides a method for constructing a model for a saturated configuration, by means of the mapping $\ValC$.

@@

%An evaluation of the efficiency of the procedure is described by Barrett et
%al.\ \cite{barrett-et-al-2007}. In particular, it is both theoretically and
%empirically beneficial to delay applications of \rn{Split} as long as
%possible. Similarly, \rn{Acyclic} and \rn{Unique} are fairly expensive because
%they require traversing the equivalence classes, which is why they are part of
%phase~2.

>>>>

\ourparagraph{Phase 2: Applying Acyclicity and Uniqueness \beforefig(\figurename~\ref{fig:ab-rules}).}
%For presentation of the rules in this phase, we rely on a representation of terms in the $\mu$-notation.
%The premises of the rules that make up the second phase refer to
We describe the rules in this phase in terms of a mapping $\Val$
that associates with each equivalence class a $\mu$-term as its representative.
%\rem{Not explicitly constructed, add here?}

@@

By Theorems~\ref{thm:t},~\ref{thm:rs}, and~\ref{thm:ss}, the
calculus is sound and complete for the universal theory of (co)datatypes. We can
rightly call it a decision procedure for that theory.
The proof of solution soundness is constructive in that it provides a
method for constructing a model for a saturated configuration, by means of the
mapping $\ValC$.

@@

As Barrett et al.\ \cite{barrett-et-al-2007} observed for their calculus,
it is both theoretically and
empirically beneficial to delay applications of \rn{Split} as long as
possible. Similarly, \rn{Acyclic} and \rn{Unique} are fairly expensive because
they require traversing the equivalence classes, which is why they are part of
phase~2.
